Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition

### 2015-07-15 papers/data_paper/datapaper.tex
finedatap

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{M59:
  An elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
  the velocity map confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{M104: 
  A lenticular/spiral galaxy with a partially depleted core \citep{jardel2011}. 
  The data within the innermost $6''.1$ are excluded from the fit, 
  and the most obvious ring of this galaxy is modeled.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M104.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-d + G-r + m-c  & $11.1$  &  $5.4$ \\
  1D eq.  & S-bul + e-d + G-r + m-c  & $52.5$  &  $7.1$ \\
  \hline
  S+11 2D         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m104}
  \tablecomments{The bulge S\'ersic index obtained by S+11 is smaller than our estimates because 
  they fit an additional nuclear component. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
  \caption{M105: 
  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
  M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R_{\rm maj} \sim 30''$.
  The velocity map shows rotation at least within $R_{\rm maj} \lesssim 30''$, 
  but no embedded disk can be recognized in the unsharp mask 
  and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
  The data within the innermost $6''.1$ are excluded from the fit.
  A single S\'ersic model does not provide a good description of the galaxy light profile.
  However, the addition of a second function (of any analytic form) to the model does not improve the fit.
  We conclude that the galaxy may not yet be fully relaxed, and we fit it with a single S\'ersic profile. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
  \caption{NGC 0821: 
  An edge-on elliptical/lenticular galaxy. 
  The ellipticity profile and the velocity map show the presence of a faint intermediate-scale disk. 
  Given its edge-on inclination, the disk is modeled with a low-$n$ S\'ersic function.   
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
  \caption{NGC 2549: 
  An edge-on barred lenticular galaxy. 
  Although the edge-on inclination of NGC 2549 complicates the identification of additional embedded components, 
  a large-scale bar ($R_{\rm maj} \lesssim 45''$) can be recognized in the galaxy image and -- more easily -- in the light profile.
  We model the large-scale bar with a Ferrer function.
  A peak in the ellipticity profile discloses the presence of a disky component
  embedded in the bulge ($R_{\rm maj} \lesssim 10''$).
  This inner component can be spotted also by looking at the velocity map, and 
  we fit it with a Ferrer function.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{NGC 3377.
  NGC 3377 is an elliptical/lenticular galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
  For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
  with a disk-to-bulge transition occurring at about $R_{\rm maj} \sim 50''$.
  \citet{arnold2014} attempted a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile 
  rather than a three-parameter $R^{1/n}$ S\'ersic function.
  Here we use a surface brightness profile twice as extended as that used by \citet{arnold2014} 
  and we identify a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component.
  The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
  and also from the ellipticity profile, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
  and then drops at larger radii.
  The nuclear stellar disk can be spotted from the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
  Each of the two disks is modelled with an exponential profile. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07 1D maj.         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11 2D         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12 2D         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14 2D         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3377}
  \tablecomments{L+14 2D obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
  \caption{NGC 3384.
  NGC 3384 is a barred lenticular galaxy that hosts 
  an embedded disk (with size $\lesssim 11''$, \citealt{erwin2004}) and 
  a nuclear stellar disk (with size $\lesssim 0''.8$, \citealt{ledo2010}).
  The isophotal parameters clearly show the presence of a boxy bar that extends out to $R_{\rm maj} \lesssim 18''$.
  We model the bar with a Ferrer function.
  An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R_{\rm maj} \sim 4''$.
  However, any attempt to account for this component resulted in a degenerate model.
  We elect not to fit neither the embedded disk nor the nuclear disk, by excluding from the fit the data within $R_{\rm maj} < 3''.7$. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
  \caption{NGC 3393.
  NGC 3393 is an edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
  circumnuclear dust \citep{martini2003}.
  The galaxy has a large-scale bar and a nuclear bar (with size $\lesssim 3''$, \citealt{erwin2004}).  
  The large-scale bar ($R_{\rm maj} \lesssim 20''$) is modeled with a Ferrer function.
  We do not model the nuclear bar and the AGN component because the poor spatial resolution of the data does not allow to fit them 
  without incurring into degeneracies.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
  \caption{NGC 3414.
  NGC 3414 is a peculiar lenticular/elliptical galaxy. 
  Different interpretations have been proposed about the morphology of this galaxy.
  \cite{whitmore1990} suggested that NGC 3414 is an spheroidal galaxy 
  with a large-scale edge-on polar ring, rather than a face-on barred lenticular galaxy.
  \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
  they cautioned against the uncertainty of their solution due to the possible misinterpretation of the galaxy morphology.
  The unsharp mask clearly shows that an embedded component does not extend all the way through the 
  center of the galaxy, but instead it is truncated at $R_{\rm maj} \sim 20''$.
  However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R_{\rm maj} \lesssim 5''$).
  The velocity map shows rotation within $R_{\rm maj} \lesssim 5''$, no rotation within $5'' \lesssim R_{\rm maj} \lesssim 15''$,
  and counterrotation beyond $R_{\rm maj} \gtrsim 15''$.
  The velocity pattern is consistent with the galaxy being a spheroidal system containing an edge-on polar ring and an edge-on nuclear disk.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3414.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
  1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
  %2D	&  & $$  & $$  &  $$ \\
  \hline
  L+10 2D         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3414}
  \tablecomments{
  L+10 2D used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
  \caption{NGC 3489.
  NGC 3489 is a barred lenticular galaxy. 
  Its disk has a smooth antitruncation at $R_{\rm maj} \sim 85''$ \citep{erwin2008}.
  %\cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
  The bar is fit with a Ferrer function.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3489.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
  1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
  2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
  \hline
  L+10 2D         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
  S+11 2D         & S-bul + e-d & $4.6$  &  $1.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3489}
  %\tablecomments{
  %S+11 2D did not fit the bar and thus obtained a larger estimate of the bulge effective radius.
  %}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
  \caption{NGC 3585. 
  NGC 3585 is an elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
  The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3585.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
  1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
  \hline
  S+11 2D         & S-bul + e-d      & $15.5$   &  $2.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3585}
  \tablecomments{
  S+11 2D obtained smaller estimates of the effective radius and S\'ersic index because
  they oversubtracted a large-scale disk.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
  \caption{NGC 3607. 
  NGC 3607 is an elliptical galaxy with an embedded disk. 
  The velocity map shows rotation only within $R_{\rm maj} \lesssim 20''$. 
   }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3607.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
  1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
  2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
  \hline
  L+10 2D	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
  S+11 2D	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
  B+12 2D	   & S-bul	      & $56.3$  &  $4.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3607}
  \tablecomments{L+10 2D obtained the smallest estimates of the effective radius and S\'ersic index because
  they oversubtracted a large-scale disk.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
  \caption{NGC 3608.
  NGC 3608 is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
  and a kinematically decoupled core. 
  We find that masking the nuclear region of this galaxy is unnnecessary and we fit the light profile with a single S\'ersic model.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3608.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul & $47.5$  &  $5.2$ \\
  1D eq.  & S-bul & $43.4$  &  $5.7$ \\
  2D      & S-bul & $62.0$  &  $7.0$ \\
  \hline
  S+11 2D         & S-bul            & $56.4$  &  $6.0$ \\
  B+12 2D         & S-bul            & $182.2$  &  $9.0$ \\
  R+13 1D eq.         & core-S\'ersic    & $56.9$  &  $6.3$ \\
  L+14 2D         & S-bul            & $48.9$  &  $6.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3608}
  \tablecomments{B+12 2D obtained the largest estimates of the effective radius and S\'ersic index, 
  possibly due to incorrect sky subtraction. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
  \caption{NGC 3842.
  NGC 3842 is the brightest member of the Leo Cluster (Abell 1367).
  It is an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013,dullograham2014cores}. %($R_{\rm break} = 0''.7$,   \citealt{rusli2013,dullograham2014cores}).
  The light profile presents a swelling at $R_{\rm maj} \sim 20''$ and the ellipticity profile has a peak in the same position.
  One can also glimpse a faint elongated oval in the unsharp mask.
  The innermost $6''.1$ are excluded from the fit.
  A single S\'ersic model is not sufficient to provide a good description of the galaxy light profile, 
  therefore we add a second component (Ferrer function) to account for the embedded lens.
  }
  \end{center}
  \end{figure}

>>>>

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
  \caption{M59:
  An elliptical galaxy with an edge-on, intermediate-scale embedded disk \citep{scorzabender1995}
  and a thin, faint nuclear stellar disk \citep{ferrarese2006acsvcs,ledo2010}. 
  The intermediate-scale embedded disk is clearly visible in our unsharp mask image (not shown), and 
  the velocity map (ATLAS$^{\rm 3D}$) confirms the presence of this rapidly rotating component, which is modeled with an exponential function.
  We choose not to account for the nuclear stellar disk by excluding the innermost $6''.1$ from the fit.  
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m104_1Dfit.eps}
  \caption{M104: 
  A lenticular/spiral galaxy with a partially depleted core \citep{jardel2011}. 
  The data within the innermost $6''.1$ are excluded from the fit, 
  and the most obvious elongated feature of this galaxy is modeled with a Ferrer function.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of M104.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-d + F-bar + m-c  & $11.0$  &  $5.8$ \\
  1D eq.  & S-bul + e-d + F-bar + m-c  & $19.6$  &  $3.7$ \\
  \hline
  S+11 2D         & S-bul + e-d + G-bar + G-n  & $66.1$  &  $1.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:m104}
  \tablecomments{The bulge S\'ersic index obtained by S+11 is smaller than our estimates because 
  they fit an additional nuclear component. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/m105_1Dfit.eps}
  \caption{M105: 
  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013}. %($R_{\rm break} = 1''.1$, \citealt{rusli2013}).
  M105 exhibits a mild isophotal twist and an abrupt change of ellipticity at $R_{\rm maj} \sim 30''$.
  The velocity map (ATLAS$^{\rm 3D}$) shows rotation at least within $R_{\rm maj} \lesssim 30''$, 
  but no embedded disk can be recognized in the unsharp mask 
  and the ellipticity profile is quite unusual for a spheroidal system with an inner disk.
  The data within the innermost $6''.1$ are excluded from the fit.
  A single S\'ersic model does not provide a good description of the galaxy light profile.
  However, the addition of a second function (of any analytic form) to the model does not improve the fit.
  We conclude that the galaxy may not yet be fully relaxed, and we fit it with a single S\'ersic profile. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n0821_1Dfit.eps}
  \caption{NGC 0821: 
  An elliptical galaxy with an edge-on embedded disk. 
  The ellipticity profile and the velocity map (ATLAS$^{\rm 3D}$, SLUGGS) show the presence of the faint intermediate-scale disk. 
  Given its edge-on inclination, the disk is modeled with a low-$n$ S\'ersic function.   
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n2549_1Dfit.eps}
  \caption{NGC 2549: 
  An edge-on barred lenticular galaxy. 
  Although the edge-on inclination of NGC 2549 complicates the identification of additional embedded components, 
  a large-scale bar ($R_{\rm maj} \lesssim 45''$) can be recognized in the galaxy image and -- more easily -- in the light profile.
  We model the large-scale bar with a Ferrer function.
  A peak in the ellipticity profile discloses the presence of a disky component
  embedded in the bulge ($R_{\rm maj} \lesssim 10''$).
  This inner component can be spotted also by looking at the velocity map (ATLAS$^{\rm 3D}$), and 
  we fit it with a Ferrer function.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
  \caption{NGC 3377: 
  An elliptical galaxy with an intermediate-scale disk and a nuclear stellar disk \citep{ledo2010}. 
  For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
  with a disk-to-bulge transition occurring at about $R_{\rm maj} \sim 50''$.
  \citet{arnold2014} attempted a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
  but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ function 
  rather than a three-parameter $R^{1/n}$ S\'ersic function.
  Here we use a surface brightness profile twice as extended as that used by \citet{arnold2014} 
  and we identify a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component.
  The presence of the intermediate-scale disk is also evident in the unsharp mask of the image mosaic 
  and also from the ellipticity, which increases with increasing radius until $R_{\rm maj} \sim 45''$ 
  and then drops at larger radii.
  The nuclear stellar disk can be spotted from the peak at $R_{\rm maj} \sim 5''$ in the $B4$ profile.
  Each of the two disks is modelled with an exponential profile. 
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3377.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + 2 e-id     & $61.8$  &  $7.7$ \\
  1D eq.  & S-bul + 2 e-id     & $91.7$  &  $9.2$ \\
  2D      & S-bul + e-id + m-n & $71.8$  &  $3.7$ \\
  \hline
  GD07 1D maj.         & S-bul     		     & $44.1$  &  $3.0$ \\
  S+11 2D         & S-bul     		     & $55.2$  &  $6.0$ \\
  B+12 2D         & S-bul     		     & $43.5$  &  $3.5$ \\
  L+14 2D         & S-bul + e-id + e-d + S-halo & $10.1$  &  $6.0$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3377}
  \tablecomments{L+14 obtained the smallest estimate of the effective radius because they oversubtracted a halo.   
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3384_1Dfit.eps}
  \caption{NGC 3384: 
  A barred lenticular galaxy that hosts 
  an embedded disk (with size $\lesssim 11''$, \citealt{erwin2004}) and 
  a nuclear stellar disk (with size $\lesssim 0''.8$, \citealt{ledo2010}).
  The isophotal parameters show clearly the presence of a boxy bar that extends out to $R_{\rm maj} \lesssim 18''$.
  We model the bar with a Ferrer function.
  An embedded disk can be seen in the unsharp mask and produces the peak in the ellipticity profile at $R_{\rm maj} \sim 4''$.
  However, any attempt to account for this component resulted in a degenerate model.
  We elect to fit neither the embedded disk nor the nuclear disk, by excluding from the fit the data within $R_{\rm maj} < 3''.7$. 
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3393_1Dfit.eps}
  \caption{NGC 3393: 
  An edge-on spiral galaxy hosting a Seyfert AGN \citep{diaz1988n3393} and 
  circumnuclear dust \citep{martini2003}.
  The galaxy has a large-scale bar and a nuclear bar (with size $\lesssim 3''$, \citealt{erwin2004}).  
  The large-scale bar ($R_{\rm maj} \lesssim 20''$) is modeled with a Ferrer function.
  We do not model the nuclear bar and the AGN component because the poor spatial resolution of the data does not allow to fit them.
  }
  \end{center}
  \end{figure}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3414_1Dfit.eps}
  \caption{NGC 3414: 
  A peculiar lenticular/elliptical galaxy. 
  Different interpretations have been proposed about the morphology of this galaxy.
  \cite{whitmore1990} suggested that NGC 3414 is a spheroidal galaxy 
  with a large-scale edge-on polar ring, rather than a face-on barred lenticular galaxy.
  \cite{laurikainen2010} decomposed NGC 3414 as a barred lenticular galaxy, but 
  they cautioned against the uncertainty of their solution due to the possible misinterpretation of the galaxy morphology.
  The unsharp mask clearly shows that an embedded component does not extend all the way through the 
  center of the galaxy, but instead it is truncated at $R_{\rm maj} \sim 20''$.
  However, an elongated structure in the galaxy center resembles a nuclear edge-on disk ($R_{\rm maj} \lesssim 5''$).
  The velocity map (ATLAS$^{\rm 3D}$) shows rotation within $R_{\rm maj} \lesssim 5''$, no rotation within $5'' \lesssim R_{\rm maj} \lesssim 15''$,
  and counterrotation beyond $R_{\rm maj} \gtrsim 15''$.
  The velocity pattern is consistent with the galaxy being a spheroidal system containing an edge-on polar ring and an edge-on nuclear disk.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3414.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id + G-r & $28.0$  &  $4.8$ \\
  1D eq.  & S-bul + e-id + G-r & $25.5$  &  $4.5$ \\
  %2D	&  & $$  & $$  &  $$ \\
  \hline
  L+10 2D         & S-bul + e-d + F-bar	  & $5.0$  &  $2.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3414}
  \tablecomments{
  L+10 used a model with a large-scale exponential disk, thus they obtained a smaller bulge effective radius and S\'ersic index.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3489_1Dfit.eps}
  \caption{NGC 3489: 
  A barred lenticular galaxy. 
  Its disk has a smooth anti-truncation at $R_{\rm maj} \sim 85''$ \citep{erwin2008}.
  %\cite{nowak2010n3368n3489} argued for the presence of both a pseudo-bulge and a classical bulge. 
  The bar is fit with a Ferrer function.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3489.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-d + F-bar & $2.2$  &  $1.5$ \\
  1D eq.  & S-bul + e-d + F-bar & $1.7$  &  $1.3$ \\
  2D      & S-bul + e-d + G-bar & $1.7$  &  $2.1$ \\
  \hline
  L+10 2D         & S-bul + e-d + F-bar & $2.0$  &  $2.1$ \\
  S+11 2D         & S-bul + e-d & $4.6$  &  $1.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3489}
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3585_1Dfit.eps}
  \caption{NGC 3585: 
  An elliptical galaxy with an embedded disk \citep{scorzabender1995}. 
  The embedded disk is visible in the unsharp mask and modeled with an exponential function. }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3585.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id & $105.0$  &  $5.2$ \\
  1D eq.  & S-bul + e-id & $86.3$  &  $6.3$ \\
  \hline
  S+11 2D         & S-bul + e-d      & $15.5$   &  $2.5$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3585}
  \tablecomments{
  S+11 2D obtained smaller estimates of the effective radius and S\'ersic index because
  they included a large-scale disk in their model.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3607_1Dfit.eps}
  \caption{NGC 3607: 
  An elliptical galaxy with an embedded disk. 
  The velocity map (ATLAS$^{\rm 3D}$) shows rotation only within $R_{\rm maj} \lesssim 20''$. 
   }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3607.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + e-id & $69.3$  &  $5.5$ \\
  1D eq.  & S-bul + e-id & $65.5$  &  $5.6$ \\
  2D      & S-bul + e-id & $60.0$  &  $5.3$ \\
  \hline
  L+10 2D	   & S-bul + e-d      & $6.5$   &  $1.5$ \\
  S+11 2D	   & S-bul + G-n      & $44.6$  &  $5.0$ \\
  B+12 2D	   & S-bul	      & $56.3$  &  $4.7$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3607}
  \tablecomments{L+10 obtained the smallest estimates of the effective radius and S\'ersic index because
  they included a large-scale disk in their model.
  }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3608_1Dfit.eps}
  \caption{NGC 3608: 
  An elliptical galaxy with an unresolved partially depleted core \citep{rusli2013} 
  and a kinematically decoupled core (ATLAS$^{\rm 3D}$, SLUGGS). 
  We find that masking the nuclear region of this galaxy is unnnecessary and we fit the light profile with a single S\'ersic model.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3608.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul & $47.5$  &  $5.2$ \\
  1D eq.  & S-bul & $43.4$  &  $5.7$ \\
  2D      & S-bul & $62.0$  &  $7.0$ \\
  \hline
  S+11 2D         & S-bul            & $56.4$  &  $6.0$ \\
  B+12 2D         & S-bul            & $182.2$  &  $9.0$ \\
  R+13 1D eq.         & core-S\'ersic    & $56.9$  &  $6.3$ \\
  L+14 2D         & S-bul            & $48.9$  &  $6.6$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3608}
  \tablecomments{B+12 obtained the largest estimates of the effective radius and S\'ersic index, 
  possibly due to incorrect sky subtraction. }
  \end{table}

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{images/n3842exp_1Dfit.eps}
  \caption{NGC 3842: 
  The brightest member of the Leo Cluster (Abell 1367), 
  an elliptical galaxy with an unresolved partially depleted core \citep{rusli2013,dullograham2014cores}. %($R_{\rm break} = 0''.7$,   \citealt{rusli2013,dullograham2014cores}).
  The light profile presents a swelling at $R_{\rm maj} \sim 20''$ and the ellipticity profile has a peak in the same position.
  One can also glimpse a faint elongated oval in the unsharp mask.
  The innermost $6''.1$ are excluded from the fit.
  A single S\'ersic model is not sufficient to provide a good description of the galaxy light profile, 
  therefore we add a second component (Ferrer function) to account for the embedded lens.
  }
  \end{center}
  \end{figure}

  \begin{table}[h]
  \small
  \caption{Best-fit parameters for the spheroidal component of NGC 3842.}
  \begin{center}
  \begin{tabular}{llcc}
  \hline
  {\bf Work} & {\bf Model}   & $\bm R_{\rm e,sph}$    & $\bm n_{\rm sph}$ \\
    &  &  $[\rm arcsec]$ & \\
  \hline
  1D maj. & S-bul + F-l + m-c  & $100.7$  &  $8.1$ \\
  1D eq.  & S-bul + F-l + m-c  & $73.6$   &  $8.2$ \\
  \hline
  R+13 1D eq.         & core-S\'ersic & $58.8$  &  $6.3$ \\
  \hline
  \end{tabular}
  \end{center}
  \label{tab:n3842}
  \end{table}
